Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-19 article.tex
Non-technical section on experimental implementation

>>>>

\subsection{The Experimental Implementation}

The most widely accepted prerequisites to build a viable physical quantum computing technology were proposed by the American physicist
David DiVincenzo in 2000, with a few additional conditions added since. The original five DiVincenzo Criteria are:

\begin{enumerate}
\item Scalable physical system of well-characterised qubits.
\item Ability to initialize the state of the qubits to a simple fiducial state.
\item Long decoherence times, much longer than the “gate-operation” time.
\item Universal set of quantum gates.
\item Qubit-specific measurement capability.
\end{enumerate}

Now there are a number of different approaches to building physical quantum computing hardware being pursued by various research groups
and companies, each with their own pros and cons. Some of the types of implemented qubits include trapped ions, nitrogen-vacancy centres,
 quantum silicon photonics and superconducting, to name but a few. The type used here is the Xmon transmon qubit, a superconducting qubit
  built around a superconducting quantum interference device, or SQUID. Variations of the superconducting qubit are being developed by
  companies such as D-wave, IBM and Rigetti in the current race for quantum supremacy.
